\hypertarget{group__group2}{
\chapter{Introduction}
\label{group__group2}\index{Introduction@{Introduction}}
}

\begin{flushleft}
The Service Description and API Reference documents define the functions, Model, Management Information Model,
Notifications, and Configuration
of the OpenClovis Application Service Platform (ASP) services. This document is written for system integrators, designers, and
system architects. It is also intended for use by application developers who would use the
OpenClovis ASP Services to develop applications that must be highly available and manageable. 
It helps the developer understand the capabilities of the OpenClovis ASP services and the APIs that are provided by each service.
\par
You should be familiar with the OpenClovis SDK User's Guide and a good knowledge of C programming language is required as the 
APIs are defined using C language.
\end{flushleft}



\section{Service Availability Forum (SA Forum)}
\index{SA Forum@{SA Forum}}
\begin{flushleft}
The Service Availability Forum (SA Forum) is a consortium of industry-leading communications and computing companies that work together
to develop and publish high availability and management software interface specifications.  
\par
A standardization of the interface between middleware and heterogeneous resources that need to be managed 
can be established by writing software that conforms to SA Forum interface specifications.
\par
The following are the OpenClovis ASP components that are conformant with SA Forum B.01.01 specifications.
\begin{itemize}
\item Availability Management Framework (AMF)
\item Checkpoint Service (CKPT)
\item Event Manager (EM)
\item Group Membership Service (GMS) component is conformant with the SA Forum CLM version B.01.01.
\end{itemize}
\end{flushleft}




\section{Using OpenClovis Libraries}
\index{Using OpenClovis Libraries@{Using OpenClovis Libraries}}
\begin{flushleft}
The following are basics for using OpenClovis ASP Libraries described in this document:

\subsection{Include File and Library Name}
To use the APIs provided by an ASP service, the statement containing declarations of data types and function prototypes
must be included. 
\newline
For example, if your application is using a Checkpoint service API you must include the following:
\footnotesize 
\begin{verbatim} 
#include <clCkptApi.h>
\end{verbatim}
\normalsize
\par
\par
To use a particular Service API, an application must link with the corresponding 
library. 
\newline
For example, to use Log service API, your application must link with the following library:
\footnotesize 
\begin{verbatim} 
libClLogClient.a or .so
\end{verbatim}
\normalsize
\par


\subsection{Library Life Cycle}
\index{Library Life Cycle@{Library Life Cycle}}
Before you use an OpenClovis ASP library it is required to initialize the library. 
You can initialize the library using the initialize function. 
\newline
For example, the log service provides the following function to initialize the log service library.
\footnotesize 
\begin{verbatim} 
	clLogInitialize()
	\end{verbatim}
	\normalsize
	
After initializing the library you can perform the required operations. 
When you no longer need to use a library it is required to finalize the library. 
You can finalize the library using the finalize function. 
\newline
For example, the log service provides the following function to finalize the log service library.
\footnotesize 
\begin{verbatim} 
	clLogFinalize()
	\end{verbatim}
	\normalsize
The initialize and finalize functions are provided by all OpenClovis ASP libraries. 
\end{flushleft}
\subsection{Type Definitions}
The type definitions specific to a library are described within the Type Definitions section. The type definitions that are
common to all libraries are described in the Common Type Definitions chapter which is a part of this document.


\section{Header Files Naming Convention}
\index{Header Files Naming Convention@{Header Files Naming Convention}}
\begin{flushleft}
This section provides the ASP services acronym list. You can identify the header files and the library files you need 
using this list. The naming convention used for the OpenClovis header files is
\footnotesize 
\begin{verbatim} 
cl<Service Acronym>Api.h
\end{verbatim}
\normalsize

\input{sheet1.tex}

\end{flushleft}




\section{Document Organization}
\begin{flushleft}
Most of the Service Description and API Reference documents are organized into the following chapters:
\newline  
\newline
Chapter 1, Functional Overview: Provides a brief description of the functionality of the service.
\newline  
\newline
Chapter 2, Service APIs: Describes all the APIs within a service and the type definitions specific to the APIs.
\end{flushleft}

\section{Related Documents}

\begin{flushleft}
Service Description and API Reference document: is written for the knowledgeable application programmer 
who understands the basic architecture and working of the OpenClovis Application Service Platform. 
To achieve this, you can refer the following documents:
\par
OpenClovis SDK User Guide: OpenClovis SDK User's Guide provides information about OpenClovis ASP
architecture, various OpenClovis ASP components, and their interactions. This
guide helps you to configure the OpenClovis ASP components, compile, and
execute the OpenClovis ASP code to build your custom application.
\par
OpenClovis IDE User Guide: OpenClovis IDE Reference Guide describes the usage of IDE, a graphical
development environment that compliment the ASP platform. This guide helps
you to configure, compile, and execute IDE to build the application.
\end{flushleft}


\section{Documentation Conventions}
\begin{flushleft}
The Service Description and API Reference documents use different fonts and symbols to differentiate between document elements and types of information. 
Following are the convention details:
\newline\newline
\begin{tabular}{|p{2in}|p{4in}|} \hline
\textbf{Notation}&\textbf{Description}\\\hline
\tt{code} &This font denotes the C code provided in various usage scenarios.\\
\hyperlink {pagebuf102}{Cross reference} &This font denotes a hyperlink. You can click on the hyperlink text to access the reference location,
which can be either a section within the 
API Guide or a URL link. A cross reference refers to a section name accesses the first page of that section.
\\ 
\textit{Italic text} &Functions and parameters are indicated in italics.\\\hline
\end{tabular}

\end{flushleft}




\chapter{Common Type Definitions}
\section{Defines}
\index{Defines@{Defines}}
\input{sheet2.tex}


\newpage
\subsection{Error Codes}
\index{Error Codes@{Error Codes}}
\begin{tabular}{|p{2in}|p{1in}|p{2in}|} \hline
\textbf{\textit{Define}} &\textbf{\textit{Value}} &\textbf{\textit{Description}} \\\hline
CL\_\-ERR\_\-ALREADY\_\-EXIST &~0x10 &An entry is already existing.\\
CL\_\-ERR\_\-BUFFER\_\-OVERRUN &~0x0d &Buffer over run.\\
CL\_\-ERR\_\-COMMON\_\-MAX &~0xff &2$^\wedge$8-1, the max for common errors. \\
CL\_\-ERR\_\-DOESNT\_\-EXIST &~0x13 &An entry does not exist.\\
CL\_\-ERR\_\-DUPLICATE &~0x08 &Duplicate entry.\\
CL\_\-ERR\_\-INITIALIZED &~0x0c &Already initialized.\\
CL\_\-ERR\_\-INUSE &~0x15 &Resource is in use.\\
CL\_\-ERR\_\-INVALID\_\-BUFFER &~0x06 &The buffer passed in is invalid.\\
CL\_\-ERR\_\-INVALID\_\-HANDLE &~0x05 &The handle passed is invalid.\\
CL\_\-ERR\_\-INVALID\_\-PARAMETER &~0x02 &Input parameters are invalid.\\
CL\_\-ERR\_\-INVALID\_\-STATE &~0x12 &Invalid State.\\
CL\_\-ERR\_\-MUTEX\_\-ERROR &~0x18 &Thread mutex error.\\
CL\_\-ERR\_\-NO\_\-CALLBACK &~0x17 &No callback available for request.\\
CL\_\-ERR\_\-NO\_\-MEMORY &~0x01 &Memory is not available.\\
CL\_\-ERR\_\-NO\_\-OP &~0x19 &Null operation.\\
CL\_\-ERR\_\-NO\_\-RESOURCE &~0x0b &No resources.\\
CL\_\-ERR\_\-NOT\_\-EXIST &~0x04 &Requested resource does not exist.\\
CL\_\-ERR\_\-NOT\_\-IMPLEMENTED &~0x07 &The function not yet implemented.\\
CL\_\-ERR\_\-NOT\_\-INITIALIZED &~0x0e &Component not initialized.\\
CL\_\-ERR\_\-NULL\_\-POINTER &~0x03 &Input parameter is a NULL pointer.\\
CL\_\-ERR\_\-OP\_\-NOT\_\-PERMITTED &~0x20 &Requested operation is not permitted.\\
CL\_\-ERR\_\-OUT\_\-OF\_\-RANGE &~0x0a &The value of one of the parameters passed is out of range.\\
CL\_\-ERR\_\-TIMEOUT &~0x14 &Timeout.\\
CL\_\-ERR\_\-TRY\_\-AGAIN &~0x16 &Component is busy , Try again.\\
CL\_\-ERR\_\-UNSPECIFIED &~0x11 &Unknown/Unspecified error.\\
CL\_\-ERR\_\-VERSION\_\-MISMATCH &~0x0f &Version mismatch.\\\hline
\end{tabular}



\newpage

\section{Typedefs}
\index{Typedefs@{Typedefs}}
\begin{tabular}{|p{2in}|p{1in}|p{2in}|} \hline
\textbf{\textit{Typedef}} &\textbf{\textit{Value}} &\textbf{\textit{Description}} \\\hline
signed long long Cl\-Uint64T &\_\-\_\-attribute\_\-\_\- ((\_\-\_\-aligned\_\-\_\-(8))) &Unsigned Long Long, 64-bit.\\
Cl\-Int8T &$\ast$ Cl\-Addr\-T &This can be used for storing address.\\
Cl\-Uint16T &Cl\-Bool\-T &This can be used for storing boolean datatype.\\
char &Cl\-Char\-T &This can be used for strings.\\
Cl\-Int32T &Cl\-Handle\-T &This can be used for storing handle.\\
signed short &Cl\-Int16T &Signed integer, 16-bit.\\
signed int &Cl\-Int32T &Signed Integer, 32-bit.\\
signed char &Cl\-Int8T &Signed Integer, 8-bit.\\
Cl\-Uint64T &Cl\-Invocation\-T &This can be used for storing invocation type.\\
Cl\-Uint64T &Cl\-Ntf\-Identifier\-T &This can be used for storing identifier.\\
Cl\-Uint64T &Cl\-Offset\-T &This can be used for storing offset.\\
void $\ast$ &Cl\-Ptr\-T &This can be used for storing pointer.\\
Cl\-Uint32T &Cl\-Rc\-T &OpenClovis return code type.\\
Cl\-Uint64T &Cl\-Selection\-Object\-T &This can be used for storing selection object.\\
Cl\-Uint64T &Cl\-Size\-T &This can be used for storing size.\\
Cl\-Int64T &Cl\-Time\-T &This can be used for storing time.\\
unsigned short &Cl\-Uint16T &Unsigned, short integer, 16-bit.\\
unsigned int &Cl\-Uint32T &Unsigned Integer, 32-bit.\\
unsigned char &Cl\-Uint8T &Unsigned Integer, 8-bit.\\
union cl\_\-u64\_\-u &Cl\-Union64T &Union having different representations of 64 bit datatype.\\\hline
\end{tabular}


\newpage
\section{Enumeration \textit{ClClovisComponentT}}
\index{Enumeration \textit{ClClovisComponentT}@{Enumeration \textit{ClClovisComponentT}}}
\begin{tabular}{|p{2in}|p{1in}|p{2in}|} \hline
\textbf{\textit{Enumeration}} &\textbf{\textit{Value}} &\textbf{\textit{Description}} \\\hline
CL\_\-CID\_\-UNSPECIFIED &0x0 &Start.\\
CL\_\-CID\_\-OSAL &0x01 &OS Abstraction Layer.\\
CL\_\-CID\_\-HAL &0x02 &Hardware Abstraction Layer.\\
CL\_\-CID\_\-DBAL &0x03 &Database Abstraction Layer.\\
CL\_\-CID\_\-EO &0x04 &Execution Object.\\
CL\_\-CID\_\-IOC &0x05 &Intelligent Object Communication.\\
CL\_\-CID\_\-RMD &0x06 &Remote Method Dispatch.\\
CL\_\-CID\_\-NAMES &0x07 &Name Service.\\
CL\_\-CID\_\-TIMER &0x08 &Timer.\\
CL\_\-CID\_\-SHM &0x09 &Shared Memory Support.\\
CL\_\-CID\_\-DSHM &0x0a &Distributed Shared Memory.\\
CL\_\-CID\_\-LOG &0x0b &Logging.\\
CL\_\-CID\_\-TRACE &0x0c &Tracing.\\
CL\_\-CID\_\-DIAG &0x0d &Diagnostics.\\
CL\_\-CID\_\-DEBUG &0x0e &Debug.\\
CL\_\-CID\_\-CPM &0x0f &Component Management.\\
CL\_\-CID\_\-CAP &0x10 &Capability Management.\\
CL\_\-CID\_\-RES &0x11 &Resource Management.\\
CL\_\-CID\_\-GMS &0x12 &Group Membership Service.\\
CL\_\-CID\_\-EVENTS &0x13 &Event Messaging.\\
CL\_\-CID\_\-DLOCK &0x14 &Distributed Locking.\\
CL\_\-CID\_\-TXN &0x15 &Transactions.\\
CL\_\-CID\_\-CKPT &0x16 &Checkpointing.\\
CL\_\-CID\_\-COR &0x17 &Clovis Object Registry.\\
CL\_\-CID\_\-CNT &0x18 &Containers.\\
CL\_\-CID\_\-DCNT &0x19 &Distributed Containers.\\
CL\_\-CID\_\-RCNT &0x1a &Resilient Containers.\\
CL\_\-CID\_\-ALARMS &0x1b &Alarm.\\
CL\_\-CID\_\-POLICY &0x1c &Policy Engine .\\
CL\_\-CID\_\-RULE &0x1d &Rule Base Engine.\\
CL\_\-CID\_\-SCRIPTING &0x1e &Scripting Engine.\\
CL\_\-CID\_\-CM &0x1f &Chassis Manager.\\
CL\_\-CID\_\-HPI &0x20 &Hardware Platform Interface.\\
CL\_\-CID\_\-FAULTS &0x21 &Fault Management.\\
CL\_\-CID\_\-AMS &0x22 &Availability Management.\\
CL\_\-CID\_\-MED &0x23 &Mediation.\\
CL\_\-CID\_\-BUFFER &0x24 &Buffer Management.\\
CL\_\-CID\_\-QUEUE &0x25 &Queue Management.\\
CL\_\-CID\_\-CLIST &0x26 &Circular List Management.\\
CL\_\-CID\_\-SNMP &0x27 &SNMP Agent.\\
CL\_\-CID\_\-NS &0x28 &Name Service.\\
CL\_\-CID\_\-OM &0x29 &Object Manger.\\
CL\_\-CID\_\-POOL &0x2a &Pool management.\\
CL\_\-CID\_\-CD &0x2b &Common Diagnostics.\\
CL\_\-CID\_\-DM &0x2c &Diagnostics Manager.\\
CL\_\-CID\_\-OAMP\_\-RT &0x2d &OAMP RT parser.\\
CL\_\-CID\_\-PROV &0x2e &provisioning Manger.\\
CL\_\-CID\_\-UM &0x2f &upgrade manager.\\\hline
\end{tabular}



\begin{tabular}{|p{2in}|p{1in}|p{2in}|} \hline
\textbf{\textit{Enumeration}} &\textbf{\textit{Value}} &\textbf{\textit{Description}} \\\hline

CL\_\-CID\_\-HANDLE &0x30 &handle database.\\
CL\_\-CID\_\-VERSION &0x31 &version checker library.\\
CL\_\-CID\_\-XDR &0x32 &xdr library.\\
CL\_\-CID\_\-IDL &0x33 &IDL.\\\hline
\end{tabular}
\newpage


\section{Data Structures}
\index{Data Structures@{Data Structures}}
\subsection{ClNameT}
\textit{typedef struct \{}
\newline \textit{ClUint16T length;}
\newline \textit{ClCharT value \mbox{[}CL\_\-MAX\_\-NAME\_\-LENGTH\mbox{]};}
\newline \textit{\} ClNameT;}
\newline
\newline 
The structure \textit{ClNameT} contains the name of the service. Its attributes are:
\begin{itemize}
\item
\textit{length} - Length of the name in bytes excluding the terminating NULL character.
\item
\textit{value} - Actual name.
\end{itemize}


\subsection{ClVersionT}

\textit{typedef struct \{}
   \newline \textit{ ClUint8T  releaseCode; } 
   \newline \textit{ ClUint8T  majorVersion; }
   \newline \textit{ ClUint8T  minorVersion;} 
\newline \textit{\} ClVersionT;}
The structure \textit{ClVersionT} contains the version information for various services. Its attributes are:
\begin{itemize}
\item
\textit{releaseCode} - Single ASCII capitol letter "A-Z." 
\item
\textit{majorVersion} - Major Number in range of [01-255].
\item
\textit{minorVersion} - Minor Number in range of [01-255].
\end{itemize}


\chapter{List of Service Description and API Reference Documents}
\index{Service Description and API Reference Documents@{Service Description and API Reference Documents}}
\begin{tabular}{|p{4in}|p{1in}|} \hline
\textbf{\textit{Service Description and API Reference Documents}} &\textbf{\textit{Version}}\\\hline
Service Description and API Reference for Alarm Service &0.3\\
Service Description and API Reference for Availability Management Service &0.3\\
Service Description and API Reference for Buffer Management Service &0.3\\
Service Description and API Reference for Checkpointing Service &0.3\\
Service Description and API Reference for Checksum Management Service &0.3\\
Service Description and API Reference for Chassis Management Service &0.3\\
Service Description and API Reference for Circular List Management Service &0.3\\
Service Description and API Reference for Container Management Service &0.4\\
Service Description and API Reference for Clovis Object Registry (COR) Service &0.3\\
Service Description and API Reference for Component Management Service &0.3\\
Service Description and API Reference for Database Abstraction Layer (DBAL) Service &0.3\\
Service Description and API Reference for Debug Service &0.3\\
Service Description and API Reference for Execution Object (EO) Service &0.3\\
Service Description and API Reference for Event Service &0.3\\
Service Description and API Reference for Fault Service &0.3\\
Service Description and API Reference for Group Membership Service &0.4\\
Service Description and API Reference for Heap Service &0.5\\
Service Description and API Reference for Interface Definition Language (IDL) Service &0.3\\
Service Description and API Reference for Intelligent Object Communication (IOC) Service &0.4\\
Service Description and API Reference for Log Service &0.4\\\hline
\end{tabular}

\begin{tabular}{|p{4in}|p{1in}|} \hline
\textbf{\textit{Service Description and API Reference Documents}} &\textbf{\textit{Version}}\\\hline
Service Description and API Reference for Mediation Management Service &0.3\\
Service Description and API Reference for Name Service &0.3\\
Service Description and API Reference for Operating System Abstraction Layer (OSAL) Service &0.3\\
Service Description and API Reference for Queue Management Service &0.3\\
Service Description and API Reference for Remote Method Dispatch (RMD) Service &0.3\\
Service Description and API Reference for Rule Based Engine (RBE) Service &0.3\\
Service Description and API Reference for Timer Service &0.3\\
Service Description and API Reference for Transaction Management Service &0.3\\\hline
\end{tabular}

